Psychological Needs During Intergroup Contact

### 2022-03-11 Methods-and-Results.Rmd
OSF data export added

```{robustForestPltComb, include=FALSE}
effRobust <- rbind(
  robustMetaContact$eff %>%
    filter(coef != "(Intercept)") %>%
    mutate(analysis = "(A) Contact and Need Fulfillment",
           metaId = paste(coef, analysis, sep = ".")),
  robustMetaSDT$eff %>%
    mutate(analysis = "(B) Other Needs",
           metaId = paste(coef, analysis, sep = "."))
)

@@

>>>>

```{r robustForestPltComb, include=FALSE}
effRobust <- rbind(
  robustMetaContact$eff %>%
    filter(coef != "(Intercept)") %>%
    mutate(analysis = "(A) Contact and Need Fulfillment",
           metaId = paste(coef, analysis, sep = ".")),
  robustMetaSDT$eff %>%
    mutate(analysis = "(B) Other Needs",
           metaId = paste(coef, analysis, sep = "."))
)

@@

```{r OsfExport, include=FALSE}
# export individual minimal CSV files 
# STUDY 1:
write.csv(
  dtWorkerSupp$workerInteractionType %>%
    select(
      "PID",
      "keyMotiveFulfilled",
      "competence.daily.all",
      "autonomy.daily.all",
      "relatedness.daily.all",
      "thermometerDutch_1",
      "keymotive_fulfillemt_1",
      "competence_1",
      "autonomy_1",
      "relatedness_1",
      "quality_overall_1",
      "OutgroupInteraction",
      "NonOutgroupInteraction"
    ),
  file = "OSF Files/Data/Study1_minimal.csv"
)

#STUDY 2:
write.csv(
  dtStudentSupp$studentInteractionType %>%
    select(
      "PID",
      "TIDnum",
      "KeyNeedFullfillment",
      "Competence",
      "Autonomy",
      "Relatedness",
      "AttitudesDutch",
      "quality_overall",
      "OutgroupInteraction",
      "NonOutgroupInteraction"
    ),
  file = "OSF Files/Data/Study2_minimal.csv"
)

# STUDY 3:
write.csv(
  dtMedicalSupp$medicalWithinBetween %>%
    select(
      "PID",
      "TIDnum",
      "OutgroupInteraction",
      "NonOutgroupInteraction",
      "AttitudesDutch",
      "qualityOverall",
      "AllportsCondition",
      "KeyNeedFulfillment",
      "Competence",
      "Autonomy",
      "Relatedness"
    ),
  file = "OSF Files/Data/Study3_minimal.csv"
)

# export joint minimal data as RData file 
# create environment for joint export
osfExport <- new.env()

# STUDY 1:
osfExport$dtWorkerSupp$workerInteractionType <- dtWorkerSupp$workerInteractionType %>%
  select(
    "PID",
    "keyMotiveFulfilled",
    "competence.daily.all",
    "autonomy.daily.all",
    "relatedness.daily.all",
    "thermometerDutch_1",
    "keymotive_fulfillemt_1",
    "competence_1",
    "autonomy_1",
    "relatedness_1", 
     "quality_overall_1", 
    "OutgroupInteraction",
    "NonOutgroupInteraction"
  )

osfExport$dtWorker$full <- dtWorker$full %>%
  select(
    "PID",
    "thermometerDutch_1"
  )

osfExport$dtWorkerSupp$workerAvFreQual <- dtWorkerSupp$workerAvFreQual

#STUDY 2:
osfExport$dtStudentSupp$studentInteractionType <- dtStudentSupp$studentInteractionType %>%
  select(
    "PID",
    "TIDnum", 
    "KeyNeedFullfillment",
    "Competence",
    "Autonomy",
    "Relatedness",
    "AttitudesDutch",
    "quality_overall",
    "OutgroupInteraction",
    "NonOutgroupInteraction"
  )

osfExport$dtStudents$full <- dtStudents$full %>%
  select(
    "PID",
    "AttitudesDutch"
  )

osfExport$dtStudentSupp$studentOutgroupInteraction <- dtStudentSupp$studentOutgroupInteraction %>%
  select(
    "PID",
    "AttitudesDutch"
  )

osfExport$dtStudentSupp$studentContactFreq <- dtStudentSupp$studentContactFreq

osfExport$dtStudentSupp$studentPltIDs <- dtStudentSupp$studentPltIDs

osfExport$dtStudentSupp$studentOutPltIDs <- dtStudentSupp$studentOutPltIDs

# STUDY 3:
osfExport$dtMedicalSupp$medicalWithinBetween <- dtMedicalSupp$medicalWithinBetween %>%
  select(
    "PID",
    "TIDnum",
    "OutgroupInteraction",
    "OutgroupInteraction_cwc",
    "OutgroupInteraction_zwc",
    "NonOutgroupInteraction",
    "NonOutgroupInteraction_cwc",
    "NonOutgroupInteraction_zwc",
    "AttitudesDutch",
    "AttitudesDutch_cwc",
    "AttitudesDutch_zwc",
    "qualityOverall",
    "qualityOverall_cwc",
    "qualityOverall_zwc",
    "AllportsCondition",
    "AllportsCondition_cwc",
    "AllportsCondition_zwc",
    "KeyNeedFulfillment",
    "KeyNeedFulfillment_cwc",
    "KeyNeedFulfillment_zwc",
    "Competence",
    "Competence_cwc",
    "Competence_zwc",
    "Autonomy",
    "Autonomy_cwc", 
    "Autonomy_zwc", 
    "Relatedness",
    "Relatedness_cwc",
    "Relatedness_zwc"
  )

osfExport$dtMedicalSupp$medicalOutWithinBetween <- dtMedicalSupp$medicalOutWithinBetween %>%
  select(
    "PID",
    "TIDnum",
    "AttitudesDutch",
    "AttitudesDutch_cwc",
    "AttitudesDutch_zwc",
    "qualityOverall",
    "qualityOverall_cwc",
    "qualityOverall_zwc",
    "AllportsCondition",
    "AllportsCondition_cwc",
    "AllportsCondition_zwc",
    "KeyNeedFulfillment",
    "KeyNeedFulfillment_cwc",
    "KeyNeedFulfillment_zwc",
    "Competence",
    "Competence_cwc",
    "Competence_zwc",
    "Autonomy",
    "Autonomy_cwc", 
    "Autonomy_zwc", 
    "Relatedness",
    "Relatedness_cwc",
    "Relatedness_zwc"
  )

osfExport$dtMedical$full <- dtMedical$full %>% 
  select(
    "PID",
    "TIDnum",
    "AttitudesDutch",
    "OutgroupInteraction", 
    "NonOutgroupInteraction",
    "KeyNeedFulfillment",
    "KeyNeedFulfillment_cwc",
    "Competence",
    "Autonomy", 
    "Relatedness", 
    "AllportsCondition", 
    "qualityOverall"
  )

osfExport$dtMedicalSupp$medicalContactFreq <- dtMedicalSupp$medicalContactFreq

osfExport$dtMedicalSupp$medicalPltIDs <- dtMedicalSupp$medicalPltIDs

osfExport$dtMedicalSupp$medicalOutPltIDs <- dtMedicalSupp$medicalOutPltIDs

# Export all relevant data for OSF
save(list = ls(osfExport),
     envir = osfExport,
     file = "OSF Files/Data/wrangled.RData")
```
